---
title: "Statistical Inference Course Project Part 2"
author: "Amy Su Jiang"
date: "October 26, 2014"
output: pdf_document
---

# Basic Inferencial Data Analysis
In this exercise we analyze the ToothGrowth data in the R datasets package. The data is set of 60 observations, length of odontoblasts (teeth) in each of 10 guinea pigs at each of three dose levels of Vitamin C (0.5, 1 and 2 mg) with each of two delivery methods (orange juice or ascorbic acid).

```{r}
library(datasets)
library(ggplot2)
ggplot(data=ToothGrowth, aes(x=as.factor(dose), y=len, fill=supp)) +
    geom_bar(stat="identity",) +
    facet_grid(. ~ supp) +
    xlab("Dose in miligrams") +
    ylab("Tooth length") +
    guides(fill=guide_legend(title="Supplement type"))
```

The above diagram shows a clear positive correlation between the tooth length and the dose levels of Vitamin C, for both supplementary types.

The hypothesis test and confidence internal for the postive correlation between tooth length and the intake dose of VC (Vitamin C) is shown as follows:

```{r}
ToothVC <- subset(ToothGrowth,supp=="VC")
VCfit <- lm(len ~ dose, data=ToothVC)
summary(VCfit)
confint(VCfit)
```

The hypothesis test and confidence internal for the postive correlation between tooth length and the intake dose of OJ (Orange Juice) is shown as follows:

```{r}
ToothOJ <- subset(ToothGrowth,supp=="OJ")
OJfit <- lm(len ~ dose, data=ToothOJ)
summary(OJfit)
confint(OJfit)
```
