---
title: "Statistical Inference Course Project - Part 1"
author: "Amy Su Jiang"
date: "October 26, 2014"
output: pdf_document
---

#Simulation Exercises
In this exercise the exponential distribution is simulated in R with rexp(n, lambda) where lambda $\lambda$ is the rate parameter. The mean of exponential distribution is 1/$\lambda$ and the standard deviation is also 1/$\lambda$. In this simulation, we investigate the distribution of averages of 40 numbers sampled from exponential distribution with $\lambda$ = 0.2.

Here is the code for generating 1000 simulated averages of 40 exponentials.

```{r}
set.seed(3)
lambda <- 0.2
num_sim <- 1000
sample_size <- 40
sim <- matrix(rexp(num_sim*sample_size, rate=lambda), num_sim, sample_size)
row_means <- rowMeans(sim)
```

The distribution of sample means are shown as follows:

```{r, echo=FALSE}
# plot the histogram of averages
hist(row_means, breaks=50, prob=TRUE,
     main="Distribution of averages of samples,
     drawn from exponential distribution with lambda=0.2",
     xlab="",col="yellow")
# density of the averages of samples
lines(density(row_means), col="blue")
# theoretical center of distribution
abline(v=1/lambda, col="red")
# theoretical density of the averages of samples
xfit <- seq(min(row_means), max(row_means), length=100)
yfit <- dnorm(xfit, mean=1/lambda, sd=(1/lambda/sqrt(sample_size)))
lines(xfit, yfit, pch=22, col="red", lty=2)
# add legend
legend('topright', c("simulation", "theoretical"), lty=c(1,2), col=c("blue", "red"))
```

The distribution of sample means is centered at `r mean(row_means)` and the theoretical center of the distribution is $\lambda^{-1}$ = `r 1/lambda`. The variance of sample means is `r var(row_means)` where the theoretical variance of the distribution is $\sigma^2 / n = 1/(\lambda^2 n) = 1/(0.04 \times 40)$ = `r 1/(0.04 * 40)`. 

The above figure has shown that the distribution is about normal, according to Central Limit Theorem.

The following figure illustrates the coverage of the confidence interval for $1/\lambda = \bar{X} \pm 1.96 \frac{S}{\sqrt{n}}$

```{r, echo=FALSE}
lambda_value <- seq(4, 6, by=0.01)
coverage <- sapply(lambda_value, function(lamb) {
    mu_hats <- rowMeans(matrix(rexp(sample_size*num_sim, rate=0.2),
                               num_sim, sample_size))
    ll <- mu_hats - qnorm(0.975) * sqrt(1/lambda^2/sample_size)
    ul <- mu_hats + qnorm(0.975) * sqrt(1/lambda^2/sample_size)
    mean(ll < lamb & ul > lamb)
})

library(ggplot2)
qplot(lambda_value, coverage) + geom_hline(yintercept=0.95)
```

The 95% confidence intervals for the rate parameter ($\lambda$) to be estimated ($\hat{\lambda}$) are $\hat{\lambda}{low} = \hat{\lambda}(1 - \frac{1.96}{\sqrt{n}})$ and $\hat{\lambda}{upp} = \hat{\lambda}(1 + \frac{1.96}{\sqrt{n}})$. As shown in the above figure, the average of the sample mean falls within the confidence interval at least 95% of the time.
